Computation and comparison of the stable Northeastern US marine boundary layer

### 2020-12-01 Paper/main.tex
updated ack

This work was authored in part by the National Renewable Energy
Laboratory, operated by Alliance for Sustainable Energy, LLC, for the
U.S. Department of Energy (DOE) under Contract No. DE-AC36-
08GO28308. M. Brazell was partially funded by the Exascale Computing
Project (17-SC-20-SC), a collaborative effort of two DOE organizations
(Office of Science and the National Nuclear Security Administration).

>>>>

This work was authored in part by the National Renewable Energy
Laboratory, operated by Alliance for Sustainable Energy, LLC, for the
U.S. Department of Energy (DOE) under Contract No. DE-AC36-
08GO28308. M. Brazell was funded by the Exascale Computing
Project (17-SC-20-SC), a collaborative effort of two DOE organizations
(Office of Science and the National Nuclear Security Administration).
